Comparing Apples and Oranges in Youth Depression Treatments?

### 2024-09-22 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
Added function to extract multilevel I2

@@

# add the ns
df_mean_coefs_from_sim <- left_join(df_mean_coefs_from_sim, df_count_studies[df_count_studies$is_missing == FALSE, ] %>% 
                                        ungroup() %>% 
                                      select(condition, n),  
                                    by = "condition")
```

>>>>

###########8. Function for extracting multilevel I2 estimates

extract_i2_values <- function(list_of_models) {
  # Initialize vectors to store I2 values
  i2_level2 <- numeric(length(list_of_models))
  i2_level3 <- numeric(length(list_of_models))

  # Loop through each fitted model from the list
  for (i in seq_along(list_of_models)) {
    model <- list_of_models[[i]]

    # Calculate variance distribution using the existing function
    i2_results <- dmetar::var.comp(model)

    # Extract I2 values for level 2 and level 3 from the results
    i2_level2[i] <- as.numeric(i2_results$results$I2[2]) # I2 for level 2
    i2_level3[i] <- as.numeric(i2_results$results$I2[3]) # I2 for level 3
  }

  # Combine I2 values into a data frame
  i2_data <- data.frame(
    i2_level2 = i2_level2,
    i2_level3 = i2_level3
  )

  return(i2_data)
}

@@

# add the ns
df_mean_coefs_from_sim <- left_join(df_mean_coefs_from_sim, df_count_studies[df_count_studies$is_missing == FALSE, ] %>% 
                                        ungroup() %>% 
                                      select(condition, n),  
                                    by = "condition")

# Extract I2 values for each dataset
i2_results_all <- extract_i2_values(list_model_1_meta_reg)

# Calculate the mean and standard deviation of I2 values for each level
i2_summary_all <- data.frame(
  mean_i2_level2 = mean(i2_results_all$i2_level2, na.rm = TRUE),
  sd_i2_level2 = sd(i2_results_all$i2_level2, na.rm = TRUE),
  mean_i2_level3 = mean(i2_results_all$i2_level3, na.rm = TRUE),
  sd_i2_level3 = sd(i2_results_all$i2_level3, na.rm = TRUE)
)
